Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
correct model object names
Render images in Word document
Remove spaces in filenames and tell Rmd to display output graphic

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Five Year Impact Factor of Journal, (D) Journal Open Access Policy, (E) Year of Publication and (F) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws. Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)
pp_m_j <- pp_check(m_k)

@@

ggsave(
  filename = here("analysis/figures/Sparks et al Figure 1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 1.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks et al Figure 1.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks et al Figure 2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 2.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks et al Figure 2.eps"))
```

@@

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

ggsave(
  filename = here("analysis/figures/Sparks et al Figure 3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 3.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks et al Figure 3.eps"))
```

@@

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow. Starting with the question, determine the methodology, describe it, make it available and cite it. Data are used in analysis and any binary files or code are made available as supplements to the manuscript. Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks et al Figure 4.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks et al Figure 4.eps"),
  outfile = here("analysis/figures/Sparks et al Figure 4.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks et al Figure 4.eps"))
```

>>>>

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Five Year Impact Factor of Journal, (D) Journal Open Access Policy, (E) Year of Publication and (F) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws. Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure'}

@@

pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)
pp_m_k <- pp_check(m_k)

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
```

@@

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure'}

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

@@

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow. Starting with the question, determine the methodology, describe it, make it available and cite it. Data are used in analysis and any binary files or code are made available as supplements to the manuscript. Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```
